A Formal Model of Checked C

### 2023-01-20 sandp23/evaluation.tex
rearrange my prev commit
update.

\noindent\textbf{Overhead of only~\systemname{}.}
To verify the impact of the sandbox on the overall program runtime, we perform a NO-OP sandbox experiment.
Our goal is to measure the runtime overhead introduced ONLY by~\systemname{}.
We perform this experiment by skipping sandboxing.
Specifically, we run the completely annotated program as a regular application without any partitioning.
However, we compile the annotated program with~\systemname compiler, which will add the relevant runtime checks (\sect{subsec:compilerimple}).
We modify the instrumentation on~\code{taint}ed pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.
~\paragraph{Results:}
Our evaluation of ~\systemname{} with NO-OP Sandbox was performed on two programs with the largest overheads in our dataset. With parsons, we see an average run-time overhead of 1.94\% as is expected as parsons (($T_{Pr}$)) gave us an overhead of only 9\%. With TinyBigNum, we see an overhead of 54.7\%, and is expected referring to the figure ~\ref{fig:microbenchmarks}, as TinyBigNum is pointer intensive with pointer operations inside nested loops.     
The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.

>>>>

\noindent\textbf{Overhead of only~\systemname{}.}
To verify the impact of the sandbox on the overall program runtime, we perform a NO-OP sandbox experiment.
Our goal is to measure the runtime overhead introduced ONLY by~\systemname{}.
We perform this experiment by skipping sandboxing.
Specifically, we run the completely annotated program as a regular application without any partitioning.
However, we compile the annotated program with~\systemname compiler, which will add the relevant runtime checks (\sect{subsec:compilerimple}).
We modify the instrumentation on~\code{taint}ed pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.

Our evaluation of ~\systemname{} with NO-OP Sandbox was performed on two programs with the largest overheads in our dataset. With parsons, we see an average run-time overhead of 1.94\% as is expected as parsons (($T_{Pr}$)) gave us an overhead of only 9\%. With TinyBigNum, we see an overhead of 54.7\%, and is expected referring to the figure ~\ref{fig:microbenchmarks}, as TinyBigNum is pointer intensive with pointer operations inside nested loops.     
This shows that~\systemname{} fundamentally has the least overhead.
%The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.
%We modify the instrumentation on~\code{tainted} pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.
%The marked \textcolor{red}{red} set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.
